### 2015-02-11 README.Rmd

# qmj (Quality Minus Junk)
Authors : Ryan Kwon, Anthoney Tsou

To install the package:

```{r}
library(devtools)
install_github("rynkwn/qmj")
```

##Background
qmj implements the results and methodology of the paper Quality Minus Junk by Clifford Asness, Andrea Frazzini, Lasse Pedersen. In their paper, they use several measures to calculate the relative profitability, growth, safety, and payouts of a company, which they use to provide an overall quality score for a company.

This quality score is used to recommend which companies to buy and which to sell, by reasoning that quality companies are likely outperform the market, while "junk" companies are likely to underperform.

Here we use the equations and methods described in the paper, coupled with data scraped from reputable online sources, in order to produce quality measurements for companies listed in the Russell 3000 Index.

##Getting Started
In order to start you off, qmj comes equipped with several data sets, including company information, financial statements, and daily stock data. To access them, call:

```{r}
library(qmj)
data(companies) #Stores company names and tickers from the Russell 3000 index
data(financials) #Stores financial documents for the given list of companies.
data(prices) # Stores price returns and closing stock prices for the past two years.
data(quality) #Stores the quality scores and the scores of its components.

#And more detailed data sets into what makes up quality
data(profitability)
data(growth)
data(payouts)
data(safety)
```

Getting a quality data frame and a holistic summary of all its components can be done by calling

```{r}
market_data(companies, financials, prices)
```

If you're only interested in accessing certain quality factors, such as profitability, as well as what makes it up (such as gross profits over assets (GPOA), or cash flow over assets (CFOA)) call

```{r}
market_profitability(companies, financials)
```

This will return a numeric vector containing profitability z-scores for the given companies, where the nth number corresponds to the nth company.

##Analyzing Your Data
The qmj package has stored a large number of qmj objects, which store significant amounts of information about a single company and which allows more in-depth analysis of that company. Some examples of analysis follow:

```{r}
data(qmjs)
first_qmj <- qmjs[[1]]
summarize(first_qmj) # Displays key information about this qmj object.

#We're clearly missing some interesting data, but we can still 
#perform some analysis.
data(safety)

plot_safety(first_qmj, safety)

#Now let's look at a graph for quality.
data(quality)
second_qmj <- qmjs[[2]]

plot_quality(second_qmj, quality)

#What if I'm only interested in looking closely at a few companies? 
#Well, voila.
desired_companies <- c("GOOG", "IBM", "FLWS") #Returns a list containing the given qmj objects in order.
desired_qmjs <- get_qmjs(desired_companies, qmjs)

summarize(desired_qmjs[[1]])
```

But the package also provides some tools for better examining your data en masse, as opposed to individual companies.

```{r}
#Let's look at the head of our quality data frame.
data(quality)
head(quality)

#Angies has an abnormally high growth score, which is very suspicious.
#Companies that are primarily driven by a single component score 
#are suspect, so let's filter out companies that are driven by growth.
sans_growth <- filter_companies(quality, filter="growth")
head(sans_growth)

#On the other hand, if we're interested in only companies that are 
#driven by growth, we can do the following:
driven_by_growth <- filter_companies(quality, filter="growth", remove=FALSE, isolate=TRUE)
head(driven_by_growth)

#We can also remove all companies with quality scores which are 
#primarily driven by any component.
#Notice that the remove parameter is by default TRUE, and 
#isolate is by default FALSE
liberal_arts_companies <- filter_companies(quality, filter="all")
head(liberal_arts_companies)
```

##Updating your Data
If you're interested in inputting your own data, you can generate financial statements for a data frame of companies as follows:

```{r}
#companies #Your custom data frame of company names and tickers. The column name for tickers must be "ticker"
#rawdata <- get_info(companies) #Retrieves raw financial statements from google finance through the quantmod package.
#financials <- tidyinfo(rawdata) #Renders raw data in a format usable by other functions in this package.
```

get_info temporarily saves your progress to the extdata folder at all stages of its process, allowing you to resume your downloading if the process is interrupted for any reason.

###Updating Prices
Updating prices is a separate, lengthy process, and for that reason is separated from the other functions that automatically collect financial statements. To update prices, which is necessary for calculating safety measurements, call:

```{r}
# rawprices <- get_prices(companies) #Retrieves stock price data from Google Finance for listed companies for the past two years. Also saves data from the S&P 500, retrieved from Yahoo Finance.
# prices <- tidy_prices(rawprices) #Renders the raw data into a form usable by other functions in this package.
```

The get_prices function is able to save its progress as it temporarily saves its download data to the extdata folder in the package's folder.

### 2015-02-11 README.Rmd
Added plot functionality to README.Rmd

@@
 data(safety)
+```
+```{r simpleplot}
+plot_safety(first_qmj, safety)
+```
 
-plot_safety(first_qmj, safety)
-
+```{r}
 #Now let's look at a graph for quality.
@@
 second_qmj <- qmjs[[2]]
+```
+```{r simpleplot}
+plot_quality(second_qmj, quality)
+```
 
-plot_quality(second_qmj, quality)
-
+```{r}
 #What if I'm only interested in looking closely at a few companies? 

### 2015-02-11 README.Rmd
Attempted to fix plotless problem in rmd.

@@
 ```
-```{r simpleplot}
+```{r fig.width=7, fig.width=6}
 plot_safety(first_qmj, safety)
@@
 ```
-```{r simpleplot}
+```{r fig.width=7, fig.height=6}
+library(ggplot2)
 plot_quality(second_qmj, quality)

### 2015-02-11 R/create_qmjs.R
change market payout to market payouts on everything based on grep

@@ -51,7 +51,7 @@ create_qmjs <- function(x, financials, prices){
   data_profitability <- market_profitability(x, financials)
   data_growth <- market_growth(x, financials)
   data_safety <- market_safety(x, financials, prices)
-  data_payouts <- market_payout(x, financials)
+  data_payouts <- market_payouts(x, financials)
   quality <- data_profitability$profitability + data_growth$growth + data_safety$safety + data_payouts$payouts
   
   #applies process of creating new qmj object to every company

### 2015-02-11 R/get_qmj.R

@@ -22,7 +22,7 @@ get_qmj <- function(companies,ticker,financials,prices) {
   profitability <- market_profitability(sub.comp,financials)
   growth <- market_growth(sub.comp,financials)
   safety <- market_safety(sub.comp,financials,prices)
-  payouts <- market_payout(sub.comp,financials)
+  payouts <- market_payouts(sub.comp,financials)
   
   #sums the scores
   quality <- profitability$profitability + growth$growth + safety$safety + payouts$payouts

### 2015-02-11 R/market_data.R

@@ -9,7 +9,7 @@
 #' @seealso \code{\link{market_profitability}}
 #' @seealso \code{\link{market_growth}}
 #' @seealso \code{\link{market_safety}}
-#' @seealso \code{\link{market_payout}}
+#' @seealso \code{\link{market_payouts}}
 #' @examples
 #' data(companies)
 #' data(financials)

### 2015-02-11 R/market_growth.R

@@ -10,7 +10,7 @@
 #' @seealso \code{\link{market_data}}
 #' @seealso \code{\link{market_profitability}}
 #' @seealso \code{\link{market_safety}}
-#' @seealso \code{\link{market_payout}}
+#' @seealso \code{\link{market_payouts}}
 #' @examples
 #' data(companies)
 #' data(financials)

### 2015-02-11 R/market_profitability.R

@@ -8,7 +8,7 @@
 #' @seealso \code{\link{market_data}}
 #' @seealso \code{\link{market_growth}}
 #' @seealso \code{\link{market_safety}}
-#' @seealso \code{\link{market_payout}}
+#' @seealso \code{\link{market_payouts}}
 #' @examples
 #' data(companies)
 #' data(financials)

### 2015-02-11 R/market_safety.R

@@ -10,7 +10,7 @@
 #' @seealso \code{\link{market_data}}
 #' @seealso \code{\link{market_profitability}}
 #' @seealso \code{\link{market_growth}}
-#' @seealso \code{\link{market_payout}}
+#' @seealso \code{\link{market_payouts}}
 #' @examples
 #' data(companies)
 #' data(financials)

### 2015-02-11 R/market_data.R
fixed example for market data

@@ -5,7 +5,7 @@
 #' for later processing.
 #' @param companies A data frame of company names and tickers.
 #' @param financials A data frame containing financial information for the given companies.
-#' @param daily A data frame containing the daily market closing prices and returns. 
+#' @param prices A data frame containing the daily market closing prices and returns. 
 #' @seealso \code{\link{market_profitability}}
 #' @seealso \code{\link{market_growth}}
 #' @seealso \code{\link{market_safety}}
@@ -13,7 +13,8 @@
 #' @examples
 #' data(companies)
 #' data(financials)
-#' market_data(companies, financials)
+#' data(prices)
+#' market_data(companies, financials, prices)
 #' @export
 
 market_data <- function(x, financials, daily){

### 2015-02-12 R/filter_companies.R
Added test to filter_companies More work done on paper.

@@ -14,6 +14,9 @@
 #' @export
 
 filter_companies <- function(data, filter, remove=TRUE, isolate=FALSE){
+  if(remove == isolate){
+    stop("Both the remove and isolate parameters are set to either true or false in filter_companies. They must have different logical values.")
+  }
   #Helper functions perform a simple arithmetic operation to determine if a given component is >= 50% of a given quality score.
   prof_filter <- function(profitability, quality){
     if(is.na(profitability) || is.na(quality)){

### 2015-02-17 R/companies.R
Explained and discuessed the Russell 3000 index in the Companies data set. Roxygenized.

@@ -2,6 +2,19 @@
 #'
 #' Stores the names and tickers for all companies in the Russell 3000 Index as of January 2015.
 #' The list from which the data was culled was last updated 6/27/2014.
+#' 
+#' The Russell 3000 Index is an equity index that tracks the performance of the 3000 largest
+#' US companies as measured by market cap. The component companies that make up this index are
+#' reconstituted once a year, usually between May and June. At this reconstitution, all companies
+#' are reranked based on their market caps for the year, and any companies which become "ineligible" by,
+#' for example, going bankrupt, becoming acquired, or becoming private, are replaced at this time.
+#' 
+#' This Index was chosen because the majority of the information used in this package relies on
+#' data sources that are US-centric, in addition to giving reasonable output by using companies which
+#' are at least of sufficient size to produce less erroneous items
+#' (such as a tiny company doubling in profitability, though the actual change is very small in magnitude)
+#' as well as producing items which are more likely to interest the user.
+#' 
 #' @format A data frame with 2999 rows and 2 variables.
 #' \itemize{
 #'    \item name = The name of the company.

### 2015-02-17 tests/testthat/test_valid_ticker.R
testing more explicitly

@@ -1,5 +1,5 @@
 test_that("ticker is valid", {
   x <- data.frame(name = "test", ticker = "TICK9")
-  expect_warning(qmj::get_info(x))
+  expect_warning(qmj::get_info(x),"parameter requires a ticker column.")
   expect_warning(qmj::get_prices(x))
 })

### 2015-02-17 R/companies.R
Companies.RData now has ticker in the first column, now ordered alphabetically by ticker.

@@ -17,8 +17,8 @@
 #' 
 #' @format A data frame with 2999 rows and 2 variables.
 #' \itemize{
-#'    \item name = The name of the company.
-#'    \item ticker = The ticker of the company.
+#'    \item name = The name of the company. Of class \code{"character"}.
+#'    \item ticker = The ticker of the company. Of class \code{"character"}.
 #'  }
 #' @source \url{https://www.russell.com/documents/indexes/membership/membership-russell-3000.pdf}
 #' @name companies

### 2015-02-27 R/qmj-class.R
modified s4 class to use ggplot2:: to eventually use imports

@@ -392,11 +392,11 @@ setMethod(f="plot_quality",
                           
                           print("Selected object is in the yellow bin.")
                           ggplot2::ggplot(df, aes(x=quality)) +
-                            ggtitle("Quality Histogram") + 
-                            xlab("Quality Scores") +
-                            ylab("Frequency") +
-                            geom_histogram(data=subset(df, cond==FALSE), binwidth=pbinwidth, origin=min, fill="black") +
-                            geom_histogram(data=subset(df, cond==TRUE), binwidth=pbinwidth, origin=min, fill="gold")
+                            ggplot2::ggtitle("Quality Histogram") + 
+                            ggplot2::xlab("Quality Scores") +
+                            ggplot2::ylab("Frequency") +
+                            ggplot2::geom_histogram(data=subset(df, cond==FALSE), binwidth=pbinwidth, origin=min, fill="black") +
+                            ggplot2::geom_histogram(data=subset(df, cond==TRUE), binwidth=pbinwidth, origin=min, fill="gold")
                         }
                       }
                       )
@@ -447,11 +447,11 @@ setMethod(f="plot_profitability",
               
               print("Selected object is in the yellow bin.")
               ggplot2::ggplot(df, aes(x=profitability)) +
-                ggtitle("Profitability Histogram") + 
-                xlab("Profitability Scores") +
-                ylab("Frequency") +
-                geom_histogram(data=subset(df, cond==FALSE), binwidth=pbinwidth, origin=min, fill="black") +
-                geom_histogram(data=subset(df, cond==TRUE), binwidth=pbinwidth, origin=min, fill="gold")
+                ggplot2::ggtitle("Profitability Histogram") + 
+                ggplot2::xlab("Profitability Scores") +
+                ggplot2::ylab("Frequency") +
+                ggplot2::geom_histogram(data=subset(df, cond==FALSE), binwidth=pbinwidth, origin=min, fill="black") +
+                ggplot2::geom_histogram(data=subset(df, cond==TRUE), binwidth=pbinwidth, origin=min, fill="gold")
             }
           }
 )
@@ -502,11 +502,11 @@ setMethod(f="plot_safety",
               
               print("Selected object is in the yellow bin.")
               ggplot2::ggplot(df, aes(x=safety)) +
-                ggtitle("Safety Histogram") + 
[…]

### 2015-03-14 R/qmj-class.R
fixing vignette as well as importing issues

@@ -44,6 +44,8 @@
 #' @slot pNPOP Object of class \code{"numeric"}. Total net payouts over profits for payouts calculation.
 #' @slot quality Object of class \code{"numeric"}. The quality score.
 #' @name qmj
+#' 
+#' @importFrom ggplot2 ggplot aes
 #' @rdname qmj-class
 #' @aliases qmj-class
 #' @exportClass qmj

### 2015-03-15 README.Rmd
modified readme file

@@
 # qmj (Quality Minus Junk)
-Authors : Ryan Kwon, Anthoney Tsou
+Authors : Anthoney Tsou, David Kane, Ryan Kwon
 
@@
 ```{r fig.width=7, fig.height=6}
-library(ggplot2)
 plot_quality(second_qmj, quality)

### 2015-04-01 TODO.Rmd

# To-Do List

* Use permanent e-mails instead of Williams e-mails.

### 2015-04-01 TODO.Rmd
more TODOs

@@
 * Use permanent e-mails instead of Williams e-mails.
+* Transfer any undone TODOs from that other system over hear.
+* Format vignette as The R Journal submission
+* Improve Description in DESCRIPTION file. This material will also be useful in the abstract of the paper.
+* Maybe help(package = "qmj") ought to produce something a bit nicer? Not sure about this.
+* Set examples to don't run (or something along that line) since they take an absurd amount of time to run and, therefore, make the default running of R CMD check impossible.
+* Get rid of lots of useless functions like view_growth and plot_quality. This is overkill. We might use versions of these functions in the article. But we don't need them to be user functions.
+* Add Quantitative Value book to bibliography.
+* Add some articles from The R Journal about finance backages, including backtest, to the bibliography.

### 2015-04-01 R/get_raw_financials.R
removed raw functions

@@ -1,13 +1,0 @@
-#' Gets raw financial statements from the extdata folder of the package.
-#'
-#' Retrieves raw data for financial statements as returned by the quantmod package.
-#' Structured as a list of three elements, which each element contains either balance sheets,
-#' cash flows, or income statements for all companies.
-#' @export
-
-get_raw_financials <- function(){
-  filepath <- system.file("extdata", package="qmj")
-  filepath <- paste(filepath, "/rawfinancials.RData", sep='')
-  load(filepath)
-  rawfinancials
-}

### 2015-04-01 R/get_raw_prices.R

@@ -1,12 +1,0 @@
-#' Gets raw price data from the extdata folder of the package.
-#'
-#' Retrieves raw data for stock price returns and closing prices. Returns a data frame, where columns
-#' are associated with a company's calculated price return and its recorded closing price for the date.
-#' @export
-
-get_raw_prices <- function(){
-  filepath <- system.file("extdata", package="qmj")
-  filepath <- paste(filepath, "/rawprices.RData", sep='')
-  load(filepath)
-  rawprices
-}

### 2015-04-02 TODO.Rmd
update

--- 2015-04-01 TODO.Rmd
@@
 
-* Use permanent e-mails instead of Williams e-mails.
+* Format vignette as The R Journal submission
+* Make examples run quickly
+* Get rid of lots of useless functions like view_growth and plot_quality. This is overkill. We might use versions of these functions in the article. But we don't need them to be user functions.
+* Get rid of qmj class material.
+* Fix NOTE about the misuse of Imports
+* Take care of issues raised in R CMD check.

### 2015-04-02 R/companies.R
removed some more unncessary examples

@@ -30,7 +30,6 @@
 #' @name companies
 #' @seealso \code{\link{financials}}
 #' @seealso \code{\link{prices}}
-#' @seealso \code{\link{quality}}
 #' @seealso \code{\link{get_info}}
 #' @seealso \code{\link{tidyinfo}}
 #' @seealso \code{\link{get_prices}}
@@ -41,13 +40,6 @@
 #' data(prices)
 #' sub_comps <- companies[50:51,]
 #' market_data(sub_comps, financials, prices)
-#' 
-#' 
-#' raw_financials <- get_info(sub_comps)
-#' usable_financials <- tidyinfo(raw_financials)
-#' 
-#' raw_prices <- get_prices(sub_comps)
-#' usable_prices <- tidy_prices(raw_prices)
 #' @docType data
 #' @keywords data
 NULL

### 2015-04-02 R/financials.R

@@ -55,7 +55,6 @@
 #' @name financials
 #' @seealso \code{\link{companies}}
 #' @seealso \code{\link{prices}}
-#' @seealso \code{\link{quality}}
 #' @seealso \code{\link{get_info}}
 #' @seealso \code{\link{tidyinfo}}
 #' @seealso \code{\link{market_data}}
@@ -63,11 +62,8 @@
 #' data(companies)
 #' data(financials)
 #' data(prices)
-#' market_data(companies, financials, prices)
-#' 
 #' sub_comps <- companies[50:51,]
-#' raw_financials <- get_info(sub_comps)
-#' usable_financials <- tidyinfo(raw_financials)
+#' market_data(sub_comps, financials, prices)
 #' @docType data
 #' @keywords data
 NULL

### 2015-04-02 R/prices.R

@@ -32,7 +32,6 @@
 #' @source Google Finance, accessed through quantmod
 #' @name prices
 #' @seealso \code{\link{companies}}
-#' @seealso \code{\link{quality}}
 #' @seealso \code{\link{financials}}
 #' @seealso \code{\link{market_data}}
 #' @seealso \code{\link{market_safety}}
@@ -44,11 +43,6 @@
 #' data(prices)
 #' sub_comps <- companies[50:51,]
 #' new_quality <- market_data(sub_comps, financials, prices)
-#' 
-#' safety_score <- market_safety(sub_comps, financials, prices)
-#' 
-#' raw_price_data <- get_prices(sub_comps)
-#' usable_price_data <- tidy_prices(raw_price_data)
 #' @docType data
 #' @keywords data
 NULL

### 2015-07-27 README.Rmd
change repo location
add Eugene

@@
 # qmj (Quality Minus Junk)
-Authors : Anthoney Tsou, David Kane, Ryan Kwon
+Authors : Anthoney Tsou, Eugene Choe, David Kane, Ryan Kwon
 
@@
 library(devtools)
-install_github("rynkwn/qmj")
+install_github("anttsou/qmj")
 ```
@@
 qmj implements the results and methodology of the paper Quality Minus Junk by Clifford Asness, Andrea Frazzini, Lasse Pedersen.
-In their paper, they use several measures to calculate the relative profitability, growth, safety, and payouts of a company, which they use to provide an overall quality score for a company.
+They use several measures to calculate scores for the relative profitability, growth, safety, and payouts of a company.
+Combining those scores generates an overall quality score.
 
-This quality score is used to recommend which companies to buy and which to sell, by reasoning that quality companies are likely outperform the market, while "junk" companies are likely to underperform.
+High quality companies are likely outperform the market, while ``junk'' companies are likely to underperform.
 
-Here we use the equations and methods described in the paper, coupled with data scraped from reputable online sources, in order to produce quality measurements for companies listed in the Russell 3000 Index.
+Here we use the equations and methods described in the paper, coupled with data scraped from online sources, in order to produce quality measurements for companies listed in the Russell 3000 Index.
 

### 2015-07-28 R/filter_companies.R
removed filter companies

@@ -1,116 +1,0 @@
-#' Filters quality data to isolate or remove companies which have quality scores that are primarily "driven" by a single component.
-#'
-#' Taking in the quality data frame and a filter parameter, returns companies that are defined to be driven by that particular
-#' factor. For a company to be driven by a particular component, at least 50% of its quality score must be due to that particular
-#' component. Also allows for the user to trim "driven" companies, returning companies that have scores that are relatively well-distributed.
-#' @param quality The quality data frame produced by market_data.
-#' @param filter What driver to search for. Valid inputs are "profitability", "growth", "payouts", "safety", and "all", which filters companies that are driven by any component.
-#' @param remove A logical value. If true, removes companies from data frame that are driven by the given filter. Mutually exclusive with the isolate parameter.
-#' @param isolate A logical value. If true, returns companies that are driven by the given filter. Mutually exclusive with the remove parameter.
-#' @examples
-#' filter <- "all"
-#' filter_companies(qmjdata::quality,filter)
-#' @export
-
-filter_companies <- function(quality = qmjdata::quality, 
-                             filter = "all", 
-                             remove = TRUE, 
-                             isolate = FALSE) {
-  if(remove == isolate) {
-    stop("Both the remove and isolate parameters are set to either true or false in filter_companies. They must have different logical values.")
-  }
-  #Helper functions perform a simple arithmetic operation to determine if a given component is >= 50% of a given quality score.
-  prof_filter <- function(profitability, data){
-    if(is.na(profitability) || is.na(data)){
-      FALSE
-    }else{
-      if(abs(profitability/data) >= .5){
-        TRUE
-      }else{
-        FALSE
-      }
-    }
-  }
-  growth_filter <- function(growth, data){
-    if(is.na(growth) || is.na(data)){
-      FALSE
-    } else{
-      if(abs(growth/data) >= .5){
-        TRUE
-      } else{
-        FALSE
-      }
-    }
-  }
-  safety_filter <- function(safety, data){
-    if(is.na(safety) || is.na(data)){
-      FALSE
-    } else{
-      if(abs(safety/data) >= .5){
-        TRUE
-      } else{
-        FALSE
-      }
-    }
-  }
-  payouts_filter <- function(payouts, data){
-    if(is.na(payouts) || is.na(data)){
-      FALSE
-    } else{
[…]

### 2015-07-28 R/market_safety.R

@@ -26,8 +26,7 @@ market_safety <- function(companies = qmjdata::companies,
   if(length(which(financials$TCSO < 0))) {
     stop("Negative TCSO exists.")
   }
-  filepath <- system.file("data", package="qmj")
-  numCompanies <- length(companies$ticker)
+  
   allcompanies <- data.frame(companies$ticker)
   colnames(allcompanies) <- "ticker"
   
@@ -49,12 +48,19 @@ market_safety <- function(companies = qmjdata::companies,
     year <- currentyear
   }
   marketlistb <- market[grepl(year,market$date),]
-  mergedail <- merge(marketlistb,nogspc,by="date")
-  splitdail <- split(mergedail,mergedail$ticker.y)
-  splitindices <- split(seq(nrow(prices)), prices$ticker)  # Stores list of indices for a company ticker.
-  #splitindices <- splitindices[-1]
-  companiesstored <- names(splitindices)
   
+  ## merge to allow cross column comparisons in price returns 
+  ## and closing prices
+  
+  mergedail <- merge(marketlistb,nogspc,by="date")
+  
+  ## separates into a list indexed by ticker
+  splitdail <- split(mergedail,mergedail$ticker.y)
+  
+  ## Stores list of indices for a company ticker.
+  splitindices <- split(seq(nrow(prices)), prices$ticker)  
+  
+  companiesstored <- names(splitindices)
   modifiedsetdiff <- function(x.1,x.2,...){
     x.1p <- do.call("paste", x.1[,1:5])
     x.2p <- do.call("paste", x.2[,1:5])
@@ -90,6 +96,7 @@ market_safety <- function(companies = qmjdata::companies,
     }
     result
   }
+  
   calc_ivol <- function(company_ticker) {
     if(length(splitdail[[company_ticker]]) > 0) {
       lmobj <- lm(as.numeric(as.character(splitdail[[company_ticker]]$pret.y))~

### 2015-07-28 R/quality.R
removed filter_companies from roxygen file

@@ -50,7 +50,6 @@
 #' @name quality
 #' @seealso \code{\link{filter_companies}}
 #' @examples
-#' filter_companies(qmjdata::quality,"all")
 #' 
 #' head(qmjdata::quality,10)
 #' 

### 2015-10-10 README.Rmd
updated readme. still needs work

@@
 data(quality) #Stores the quality scores and the scores of its components.
-
-#And more detailed data sets into what makes up quality
-data(profitability)
-data(growth)
-data(payouts)
-data(safety)
 ```
@@
 
-This will return a numeric vector containing profitability z-scores for the given companies, where the nth number corresponds to the nth company.
-
-##Analyzing Your Data
-The qmj package has stored a large number of qmj objects, which store significant amounts of information about a single company and which allows more in-depth analysis of that company.
-Some examples of analysis follow:
-
-```{r}
-data(qmjs)
-first_qmj <- qmjs[[1]]
-summarize(first_qmj) # Displays key information about this qmj object.
-
-#We're clearly missing some interesting data, but we can still 
-#perform some analysis.
-data(safety)
-```
-```{r fig.width=7, fig.width=6}
-plot_safety(first_qmj, safety)
-```
-
-```{r}
-#Now let's look at a graph for quality.
-data(quality)
-second_qmj <- qmjs[[2]]
-```
-```{r fig.width=7, fig.height=6}
-plot_quality(second_qmj, quality)
-```
-
-```{r}
-#What if I'm only interested in looking closely at a few companies? 
-#Well, voila.
-desired_companies <- c("GOOG", "IBM", "FLWS") #Returns a list containing the given qmj objects in order.
-desired_qmjs <- get_qmjs(desired_companies, qmjs)
-
-summarize(desired_qmjs[[1]])
-```
-
-But the package also provides some tools for better examining your data en masse, as opposed to individual companies.
-
-```{r}
-#Let's look at the head of our quality data frame.
-data(quality)
-head(quality)
-
-#Angies has an abnormally high growth score, which is very suspicious.
-#Companies that are primarily driven by a single component score 
-#are suspect, so let's filter out companies that are driven by growth.
-sans_growth <- filter_companies(quality, filter="growth")
-head(sans_growth)
-
-#On the other hand, if we're interested in only companies that are 
-#driven by growth, we can do the following:
-driven_by_growth <- filter_companies(quality, filter="growth", remove=FALSE, isolate=TRUE)
-head(driven_by_growth)
-
-#We can also remove all companies with quality scores which are 
-#primarily driven by any component.
-#Notice that the remove parameter is by default TRUE, and 
-#isolate is by default FALSE
-liberal_arts_companies <- filter_companies(quality, filter="all")
-head(liberal_arts_companies)
-```
+This will return a data frame containing profitability z-scores for the given companies as well as the z-scores for the components creating the profitability scores.
 
@@
 
-The get_prices function is able to save its progress as it temporarily saves its download data to the extdata folder in the package's folder.
+Similar to the get_info function, The get_prices function is also able to save its progress and resume previous downloads.

### 2015-10-10 tests/testthat/test_financials.R

@@ -6,7 +6,7 @@ prices <- qmjdata::prices
 
 test_that("tcso is positive", {
   temp <- financials
-  temp <- rbind(temp,rep(-1,length(colnames(temp))))
+  temp <- rbind(temp,rep(-1, length(colnames(temp))))
   expect_error(market_data(companies,temp,prices),"Negative TCSO exists.")
   expect_error(market_profitability(companies,temp),"Negative TCSO exists.")
   expect_error(market_growth(companies,temp),"Negative TCSO exists.")

### 2015-10-10 README.Rmd
updated readme
cleaned up readme some more

@@
 
-High quality companies are likely outperform the market, while ``junk'' companies are likely to underperform.
+High quality companies are likely outperform the market, while "junk" companies are likely to underperform.
 
@@
 ##Updating your Data
-If you're interested in inputting your own data, you can generate financial statements for a data frame of companies as follows:
+Suppose you want to use the qmj package for your a custom set of companies, a dataset we will call "custom_companies".
+You can generate the most recent financial statements for those companies as follows:
 
 ```{r}
-#companies #Your custom data frame of company names and tickers. The column name for tickers must be "ticker"
-#rawdata <- get_info(companies) #Retrieves raw financial statements from google finance through the quantmod package.
-#financials <- tidyinfo(rawdata) #Renders raw data in a format usable by other functions in this package.
+# Note that your custom data frame of company names and tickers must have the column name "ticker" for the column of tickers.
+
+## Retrieves raw financial statements from google finance through the quantmod package.
+
+rawdata <- get_info(companies)
+
+## Renders raw data in a format usable by other functions in this package and also dramatically improves readability.
+
+financials <- tidyinfo(rawdata)
+
 ```
 
-get_info temporarily saves your progress to the extdata folder at all stages of its process, allowing you to resume your downloading if the process is interrupted for any reason.
+get_info also allows you to resume your downloading if the process is interrupted for any reason.
 
-###Updating Prices
+##Updating Prices
 Updating prices is a separate, lengthy process, and for that reason is separated from the other functions that automatically collect financial statements.
@@
 ```{r}
-# rawprices <- get_prices(companies) #Retrieves stock price data from Google Finance for listed companies for the past two years. Also saves data from the S&P 500, retrieved from Yahoo Finance.
-# prices <- tidy_prices(rawprices) #Renders the raw data into a form usable by other functions in this package.
+
+## Retrieves stock price data from Google Finance for listed companies for the past two years. Also saves data from the S&P 500, retrieved from Yahoo Finance.
+
+rawprices <- get_prices(companies)
+
+## Renders the raw data into a form usable by other functions in this package.
+
+prices <- tidy_prices(rawprices) 
 ```

### 2015-10-10 README.Rmd
updated readme again

@@
 ```{r}
-# Note that your custom data frame of company names and tickers must have the column name "ticker" for the column of tickers.
+## Note that your custom data frame of company names and tickers must have the column name 
+## "ticker" for the column of tickers.
 
@@
 
-## Renders raw data in a format usable by other functions in this package and also dramatically improves readability.
+## Renders raw data in a format usable by other functions in this package 
+## and also dramatically improves readability.
 
@@
 
-## Retrieves stock price data from Google Finance for listed companies for the past two years. Also saves data from the S&P 500, retrieved from Yahoo Finance.
+## Retrieves stock price data from Google Finance for listed companies for the past two years. 
+## Also saves data from the S&P 500, retrieved from Yahoo Finance.
 

### 2015-10-10 R/tidy_prices.R
Tidy prices now cleaner. Some commenting begun.

@@ -22,34 +22,25 @@
 #' @export
 
 tidy_prices <- function(x){
-  numCompanies <- (length(names(x))/2) #Every company which has data adds two columns to the raw data output.
-  numDaysInTwoYears <- 732 #We expect at most this many days of data from a company.
-  tidymatrix <- matrix(nrow=(numDaysInTwoYears * numCompanies), ncol=4) #Output matrix is pre-allocated for speed.
-  colnames(tidymatrix) <- c("ticker", "date", "pret", "close")
-  dates <- rownames(x)
-  for(i in 1:numCompanies){
-    ticker <- gsub(".Close","",names(x)[2*i - 1]) #Parses the ticker out of one of the columns contributed by the company.
-    ticker <- gsub(".Adjusted", "", ticker) #Correctly retrieves ticker from the special case of GSPC.Adjusted (S&P 500)
-    col1 <- x[,(2*i)-1]
-    col2 <- x[,(2*i)]
-    
-    #Select only data rows which are not na.
-    nas <- which(!is.na(col1))
-    cDates <- dates[nas]
-    col1 <- col1[nas]
-    col2 <- col2[nas]
-    
-    for(k in 1:length(col1)){
-      #Loop places raw company data into expected positions in pre-allocated tidymatrix.
-      tidymatrix[k + ((i-1) * numDaysInTwoYears), 1] <- ticker
-      tidymatrix[k + ((i-1) * numDaysInTwoYears), 2] <- cDates[k]
-      tidymatrix[k + ((i-1) * numDaysInTwoYears), 4] <- col1[k]
-      tidymatrix[k + ((i-1) * numDaysInTwoYears), 3] <- col2[k]
-    }
+  colNames <- names(x)
+  closing <- x[,grep(".Close", colNames)]
+  pret <- x[,grep("pret", colNames)]
+  
+  #' @describeIn priceCombine combines relevant columns from the original price
+  #' data set.
+  priceCombine <- function(colReference){
+    dates <- rownames(closing)
+    ticker <- gsub(".Close","",names(closing)[colReference])
+    ticker <- rep(ticker, length(dates))
+    cbind(data.frame(ticker, date=dates, pret=pret[,colReference], close=closing[,colReference]))
   }
-  tidyresult <- as.data.frame(tidymatrix, stringsAsFactors=FALSE)
[…]

### 2015-10-10 README.Rmd
updated readme

@@
 library(qmj)
-data(companies) #Stores company names and tickers from the Russell 3000 index
-data(financials) #Stores financial documents for the given list of companies.
-data(prices) # Stores price returns and closing stock prices for the past two years.
-data(quality) #Stores the quality scores and the scores of its components.
+data(companies) ## Stores company names and tickers from the Russell 3000 index.
+data(financials) ## Stores financial documents for the given list of companies.
+data(prices) ## Stores price returns and closing stock prices for the past two years.
+data(quality) ## Stores the quality scores and the scores of its components.
 ```

### 2015-10-10 R/tidy_prices.R
Final comment changes. Function successfully worked.

@@ -26,19 +26,18 @@ tidy_prices <- function(x){
   closing <- x[,grep(".Close", colNames)]
   pret <- x[,grep("pret", colNames)]
   
-  #' @describeIn priceCombine combines relevant columns from the original price
+  #' @describeIn pricecombine combines relevant columns from the original price
   #' data set.
-  priceCombine <- function(colReference){
+  pricecombine <- function(colReference){
     dates <- rownames(closing)
     ticker <- gsub(".Close","",names(closing)[colReference])
     ticker <- rep(ticker, length(dates))
     cbind(data.frame(ticker, date=dates, pret=pret[,colReference], close=closing[,colReference]))
   }
   
-  data <- lapply(1:ncol(closing), priceCombine)
+  data <- lapply(1:ncol(closing), pricecombine)
   
-  ## Resulting data frames are combined by rows, and the appropriate
-  ## columns are converted into reasonable types.
+  ## Aggregate data sets and convert pret and close columns to type numeric.
   result <- dplyr::bind_rows(data)
   result$pret <- as.numeric(result$pret)
   result$close <- as.numeric(result$close)

### 2015-10-10 R/qmj.R
updated qmj documentation to remove old datasets

@@ -9,8 +9,6 @@
 #' safety, and payouts. By using publicly available data for 
 #' company balance sheets, income statements, and cash flows, the 
 #' qmj package calculates relative quality z-scores for companies. 
-#' Utility functions in the class qmj also allow users to further 
-#' analyze the quality of stocks.
 #' 
 #' All functions and datasets are documented, and are freely 
 #' available for use.
@@ -20,19 +18,9 @@
 #'  3000 Index
 #'  \item financials - financial statements for companies in the 
 #'  companies dataset
-#'  \item profitability - most recently measured profitability z-scores 
-#'  and their components
-#'  \item growth - most recently measured growth z-scores and their 
-#'  components
-#'  \item safety - most recently measured safety z-scores and their 
-#'  components
-#'  \item payouts - most recently measured payouts z-scores and their 
-#'  components
+#'  \item prices - daily prices and price returns for the past two years
 #'  \item quality - most recently measure quality z-scores and their 
 #'  components
-#'  \item qmjs - objects of class qmj, providing utility functions for 
-#'  further analysis of company quality
-#'  \item prices - daily prices and price returns for the past two years
 #' }
 #' 
 #' @references

### 2016-01-10 tests/testthat/test_financial_data_gathering_processing.R
Tests have been modified such that the ones that require an internet connection break off if no connection exists.

@@ -11,12 +11,17 @@
 #' - For any given ticker, tidied financial information has at most 4 rows.
 #'
 
-companies <- qmjdata::companies[1,]
+companies <- qmjdata::companies[1:3,]
 raw_fins <- qmj::get_info(companies)
 
 context("Gathering Raw Financial Data Tests")
 
 test_that("Missing companies are solely because quantmod provides no data", {
+  
+  ## If no data at all was gathered, assume internet connection is bad.
+  if(length(raw_fins[[1]]) == 0)
+    testthat::skip()
+  
   
   #' @describeIn Grabs the ticker from an element in one of the sublists
   #' of raw_fins
@@ -54,6 +59,10 @@ test_that("Missing companies are solely because quantmod provides no data", {
 context("Processing/Tidying Financial Data Tests")
 
 test_that("Every ticker appears in the tidied financial data set at most four times", {
+  
+  ## If no data at all was gathered, assume internet connection is bad.
+  if(length(raw_fins[[1]]) == 0)
+    testthat::skip();
 
   fins <- tidyinfo(raw_fins)
   

### 2016-01-10 tests/testthat/test_price_data_gathering_processing.R

@@ -14,10 +14,14 @@
 
 context("Gathering Raw Price Data Tests")
 
-companies <- qmjdata::companies[1,]
-raw_prices <- qmj::get_prices(companies)
+companies <- qmjdata::companies[1:3,]
+raw_prices <- tryCatch(qmj::get_prices(companies), error = function(e) e)
 
 test_that("Every ticker in the raw price data is unique with a predicted number of columns", {
+  
+  ## If error is returned, no internet connection.
+  if(inherits(raw_prices, "error"))
+    testthat::skip()
   
   ## Grab column names and remove everything but the ticker.
   tickers <- colnames(raw_prices)
@@ -40,6 +44,10 @@ test_that("Every ticker in the raw price data is unique with a predicted number 
 
 test_that("Every ticker for which we successfully grabbed data, has some data", {
   
+  ## If error is returned, no internet connection.
+  if(inherits(raw_prices, "error"))
+    testthat::skip()
+  
   #' @describeIn Check to make sure every column has at least one non-na entry
   col_check <- function(column) {
     expect_true(sum(!is.na(column)) >= 1, label="grabbed data contains some data")
@@ -51,6 +59,10 @@ test_that("Every ticker for which we successfully grabbed data, has some data", 
 })
 
 test_that("Missing Companies is Solely Due To Quantmod Finding No Data", {
+  
+  ## If error is returned, no internet connection.
+  if(inherits(raw_prices, "error"))
+    testthat::skip()
   
   ## First get all companies for which we do have data.
   tickers <- colnames(raw_prices)
@@ -94,6 +106,10 @@ test_that("Missing Companies is Solely Due To Quantmod Finding No Data", {
 context("Processing/Tidying Price Data Tests")
 
 test_that("Raw data matches processed data for any given company", {
+  
+  ## If error is returned, no internet connection.
+  if(inherits(raw_prices, "error"))
+    testthat::skip()
   
   ## Grab all .Close and pret columns from the raw data.
   close_indices <- grep('(.Close)', colnames(raw_prices))

### 2016-01-10 R/get_prices.R
Should have fixed tempdir access issue for OSX

@@ -84,7 +84,7 @@ get_prices <- function(companies = qmjdata::companies) {
   }
   
   ## Folder destination of all temp files.
-  filepath <- Sys.getenv("temp")
+  filepath <- tempdir()
   
   ## We only desire stock data for the past two years.
   startDate <- as.POSIXlt(Sys.Date())

### 2016-01-10 README.Rmd

--- 2015-10-10 README.Rmd
@@
 library(qmj)
-data(companies) #Stores company names and tickers from the Russell 3000 index
-data(financials) #Stores financial documents for the given list of companies.
-data(prices) # Stores price returns and closing stock prices for the past two years.
-data(quality) #Stores the quality scores and the scores of its components.
+companies <- qmjdata::companies ## Stores company names and tickers from the Russell 3000 index.
+financials <- qmjdata::financials ## Stores financial documents for the given list of companies.
+prices <- qmjdata::prices ## Stores price returns and closing stock prices for the past two years.
+quality <- qmjdata::quality ## Stores the quality scores and the scores of its components.
 ```

### 2016-01-13 README.Rmd
Fixed some inaccuracies in README. Alphabetized author list by last name.
Added a brief 'More Information' snippet to direct users to our vignette to find any particulars.

@@
 # qmj (Quality Minus Junk)
-Authors : Anthoney Tsou, Eugene Choe, David Kane, Ryan Kwon
+Authors : Eugene Choe, David Kane, Ryan Kwon, Anthoney Tsou
 
@@
 
-rawdata <- get_info(companies)
+rawdata <- get_info(custom_companies)
 
@@
 
-rawprices <- get_prices(companies)
+rawprices <- get_prices(custom_companies)
 
@@
 Similar to the get_info function, The get_prices function is also able to save its progress and resume previous downloads.
+
+##More Information
+More information, especially regarding methodology and what measures were used to filter out companies with bad or insufficient data, may be found in our vignette.

### 2025-01-17 README.Rmd
fixes to list on CRAN

@@
 library(qmj)
-companies <- qmjdata::companies ## Stores company names and tickers from the Russell 3000 index.
-financials <- qmjdata::financials ## Stores financial documents for the given list of companies.
-prices <- qmjdata::prices ## Stores price returns and closing stock prices for the past two years.
-quality <- qmjdata::quality ## Stores the quality scores and the scores of its components.
+companies_r3k16   ## Stores company names and tickers from the Russell 3000 index.
+financials_r3k16  ## Stores financial documents for the given list of companies.
+prices_r3k16      ## Stores price returns and closing stock prices for the past two years.
+quality_r3k16     ## Stores the quality scores and the scores of its components.
 ```
@@
 ```{r}
-market_data(companies, financials, prices)
+market_data(companies_r3k16, financials_r3k16, prices_r3k16)
 ```
@@
 ```{r}
-market_profitability(companies, financials)
+market_profitability(companies_r3k16, financials_r3k16)
 ```

### 2025-01-17 R/clean_downloads.R

@@ -27,32 +27,11 @@
 #' @seealso \code{\link{get_prices}}
 #' @seealso \code{\link{get_info}}
 #' @examples
-#' \dontrun{
-#' 
-#' ## Without a specified data frame, 
-#' ## clean_downloads defaults to the package
-#' ## provided data frame of comapnies.
-#' 
 #' clean_downloads()
 #' 
-#' ## If we wanted to remove temporarily 
-#' ## downloaded files for only some
-#' ## subset of our companies, or if we 
-#' ## wanted to specify a modified data frame
-#' ## of companies.
-#' 
-#' clean_downloads(sub_comps)
-#' 
-#' ## Fetch fresh data after removing old 
-#' ## temporary files.
-#' 
-#' get_prices(sub_comps)
-#' get_info(sub_comps)
-#' 
-#' }
 #' @export
 
-clean_downloads <- function(x = qmjdata::companies) {
+clean_downloads <- function(x = qmj::companies_r3k16) {
   tickers = x$ticker
   if (length(tickers) == 0) {
     stop("parameter requires a ticker column.")

### 2025-01-17 R/companies_r3k16.R

@@ -1,0 +1,47 @@
+#' A list of all companies in the Russell 3000 Index
+#'
+#' Stores the names and tickers for all companies in the 
+#' Russell 3000 Index as of January 2016.The list from 
+#' which the data was culled was last updated 2015/06/26.
+#' 
+#' The Russell 3000 Index is an equity index that tracks 
+#' the performance of the "3000" (this number may actually 
+#' vary from year to year, but is always in the neighborhood 
+#' of 3000) largest US companies as measured by market cap. 
+#' The component companies that make up this index are 
+#' reconstituted once a year, usually between May and June.
+#' At this reconstitution, all companies are reranked based 
+#' on their market caps for the year, and any companies which 
+#' become "ineligible" by,for example, going bankrupt, 
+#' becoming acquired, or becoming private, are replaced at 
+#' this time.
+#' 
+#' This Index was chosen due to the size of its component
+#' companies (which mitigates the likelihood of erroneous 
+#' items, such as a tiny company doubling in profitability 
+#' despite there being little absolute change), this package's 
+#' reliance on US-centric data sources, and to produce items which
+#' are more likely to interest the user.
+#' 
+#' Companies_r3k16 crucially provides tickers to many functions in the
+#' package, allowing the package to connect financial statements 
+#' and price information to a specific company. It is also the 
+#' basis of the many "get" functions of the package, which retrieves 
+#' and then formats data from the web. The Companies_r3k16 data set is the 
+#' "base" data that produces financials, prices, and ultimately 
+#' quality scores.
+#' 
+#' @format A data frame with approximately 3000 rows and 2 variables.
+#' \itemize{
+#'    \item name = The name of the company. Of class 
+#'    \code{"character"}.
+#'    \item ticker = The ticker of the company. Of class 
+#'    \code{"character"}.
+#'  }
+#' @source \url{https://www.lseg.com/en/ftse-russell}
+#' @name companies_r3k16
+#' @seealso \code{\link{financials_r3k16}}
+#' @seealso \code{\link{prices_r3k16}}
+#' @docType data
+#' @keywords data
+NULL

### 2025-01-17 R/financials_r3k16.R

@@ -1,0 +1,63 @@
+#' Financial statements of all companies in the Russell 3000 index 
+#' for the past four years
+#'
+#' A data frame containing all annual financial statements (balancesheets,
+#' cashflows, and income statements) for the past four years if available.
+#' For a description of the Russell 3000 index, as well as why it was used
+#' for this package, see \code{\link{companies_r3k16}}. Last updated 2016/01/06.
+#' 
+#' Some companies may store "weird" data, such as having information solely 
+#' for the years 1997-2001, or by having multiple annual reports within the
+#' same year (such as one report being filed in March of 2013, and another 
+#' filed in December of 2013). In the case of companies reporting multiple 
+#' annual data from the same year, the years of their reports are suffixed 
+#' with their order. For example, GOOG may have data from 2013.1, 2013.2, 
+#' 2012.3, 2011.4. This means Google's most recent data set is from 
+#' 2013 (2013.1), another data set was published in 2013 (2013.2), and the 
+#' remaining years are also suffixed for convenience.
+#' 
+#' The main purpose of financials_r3k16 is to provide key information for each 
+#' company in order to calculate each of the quality component scores 
+#' (profitability, growth, safety, and payouts). For every ticker in the 
+#' \code{\link{companies_r3k16}} data set, financials_r3k16 will try to store the most 
+#' recent four years of annual data, though this may vary based on 
+#' availability.
+#' 
+#' @format A data frame with approximately 12000 rows and 23 variables
+#'  \itemize{
+#'    \item AM = Amortization, of class \code{"character"}.
+#'    \item CWC = Changes in Working Capital, of class \code{"character"}.
+#'    \item CX = Capital Expenditures, of class \code{"character"}.
+#'    \item DIVC = Dividends per Share, of class \code{"character"}.
+#'    \item DO = Discontinued Operations, of class \code{"character"}.
+#'    \item DP.DPL = Depreciation/Depletion, of class \code{"character"}.
+#'    \item GPROF = Gross Profits, of class \code{"character"}.
+#'    \item IAT = Income After Taxes, of class \code{"character"}.
+#'    \item IBT = Income Before Taxes, of class \code{"character"}.
+#'    \item NI = Net Income, of class \code{"character"}.
+#'    \item NINT = Interest and Expense - Net Operating, of class 
[…]

### 2025-01-17 R/get_companies.R

@@ -9,7 +9,7 @@
 #' data correctly. Simply select all of the component list and paste 
 #' the contents into an empty document with
 #' the .txt extension. The list may be found 
-#' \href{https://www.russell.com/documents/indexes/membership/membership-russell-3000.pdf}{here}.
+#' \href{https://www.lseg.com/en/ftse-russell}{here}.
 #' 
 #' If you wish to use your own text file of companies for get_companies to process,
 #' create a text file containing each company on a separate line. Every word and ticker
@@ -23,24 +23,13 @@
 #' tickers of interest. May be either absolute or relative to working directory.
 #' 
 #' @examples
-#' ## The function by default uses a text 
-#' ## file created from the Russell 3000 Index.
-#' 
 #' get_companies()
 #' 
-#' ## As an example valid txt file, create 
-#' ## 'companies.txt' in our current working 
-#' ## directory containing the following two lines:
-#' ## APPLE AAPL
-#' ## GOOGLE GOOG
-#' 
-#' \dontrun{
-#' 
-#' get_companies('companies.txt')
-#' 
-#' }
-#' 
 #' @importFrom dplyr arrange
+#' @importFrom rlang .data
+#' 
+#' @return data.frame of companies info
+#' 
 #' @export
 
 get_companies <- function(filepath = system.file("extdata/companies.txt", package = "qmj")) {
@@ -76,6 +65,5 @@ get_companies <- function(filepath = system.file("extdata/companies.txt", packag
   row.names(companies) <- NULL
   
   ## Arrange alphabetically by ticker.
-  companies <- dplyr::arrange(companies, ticker)
-  companies
+  dplyr::arrange(companies, .data[["ticker"]])
 } 

### 2025-01-17 R/get_info.R

@@ -9,7 +9,7 @@
 #' data, quickly resuming its progress. Once complete, \code{get_info} deletes
 #' all used temporary data.
 #' 
-#' Parameter data frame defaults to provided \code{companies} data set if not specified.
+#' Parameter data frame defaults to provided \code{companies_r3k16} data set if not specified.
 #' 
 #' @return A list with three elements. Each element is a list containing
 #' all financial documents of a specific type for each company. These lists are, in order,
@@ -22,48 +22,17 @@
 #' @seealso \code{\link{tidyinfo}}
 #' 
 #' @examples
-#' \dontrun{
-#' 
-#' ## If no data frame is provided, 
-#' ## the default is the package's 
-#' ## companies data set.
-#' 
-#' get_info()
-#' 
-#' ## If we want to get information 
-#' ## for a specific data frame of 
-#' ## companies, called comps
-#' 
-#' get_info(comps)
-#' 
-#' ## If we then decide to quit the 
-#' ## process partway through, and 
-#' ## then resume downloading,
-#' ## the function usage is identical.
-#' 
-#' get_info(comps)
-#' 
-#' ## If we quit the process partway 
-#' ## through, and then decide to 
-#' ## clean the data to start
-#' ## from scratch.
-#' 
-#' clean_downloads(comps)
-#' get_info(comps)
-#' 
-#' ## The raw financial data is 
-#' ## difficult to use, so we'll 
-#' ## clean the data for use in 
-#' ## other functions.
-#' 
-#' fin_data <- get_info(comps)
-#' financials <- tidyinfo(fin_data)
-#' 
+#' \donttest{
+#' # Takes more than 10 secs
+#' if (reticulate::py_module_available("yfinance")) 
+#'   get_info(companies_r3k16[companies_r3k16$ticker %in% c("AAPL", "AMZN"), ])
 #' }
+#' 
 #' @importFrom quantmod getFinancials viewFinancials
+#' @importFrom reticulate py_run_string import
 #' @export
 
-get_info <- function(companies = qmjdata::companies) {
+get_info <- function(companies = qmj::companies_r3k16) {
   tickers = companies$ticker
   if (length(tickers) == 0) {
     stop("parameter requires a ticker column.")
@@ -74,55 +43,60 @@ get_info <- function(companies = qmjdata::companies) {
   listfiles <- rep("", length(tickers))
   filesInDest <- list.files(path = filepath)
   
[…]

### 2025-01-17 R/get_prices.R

@@ -27,46 +27,12 @@
 #' @seealso \code{\link{tidy_prices}}
 #' 
 #' @examples
-#' \dontrun{
+#' get_prices(companies_r3k16[companies_r3k16$ticker %in% c("AAPL", "AMZN"), ])
 #' 
-#' ## If no data frame is provided, 
-#' ## the default is the package's 
-#' ## companies data set.
-#' 
-#' get_prices()
-#' 
-#' ## If we want to get information 
-#' ## for a specific data frame of 
-#' ## companies, called comps
-#' 
-#' get_prices(comps)
-#' 
-#' ## If we then decide to quit the 
-#' ## process partway through, and 
-#' ## then resume downloading,
-#' ## the function usage is identical.
-#' 
-#' get_prices(comps)
-#' 
-#' ## If we quit the process partway 
-#' ## through, and then decide to clean 
-#' ## the data to start from scratch.
-#' 
-#' clean_downloads(comps)
-#' get_prices(comps)
-#' 
-#' ## The raw price data is difficult 
-#' ## to use, so we'll clean the data 
-#' ## for future use.
-#' 
-#' price_data <- get_prices(comps)
-#' prices <- tidy_prices(price_data)
-#' 
-#' }
 #' @importFrom quantmod getSymbols
 #' @export
 
-get_prices <- function(companies = qmjdata::companies) {
+get_prices <- function(companies = qmj::companies_r3k16) {
   numCompanies <- length(companies$ticker)
   if (numCompanies == 0) {
     stop("parameter requires a ticker column.")
@@ -118,12 +84,14 @@ get_prices <- function(companies = qmjdata::companies) {
       listfiles[i + 1] <- absoluteFilePath
       
     } else {
-      stockData <- tryCatch(quantmod::getSymbols(companyTicker, src="google", auto.assign=FALSE, from=startDate,
+      stockData <- tryCatch(quantmod::getSymbols(companyTicker, src="yahoo", auto.assign=FALSE, from=startDate,
                                                  warnings=FALSE, messages=FALSE), 
                             error = function(e) e)
       
       ## If we successfully retrieved the data, and there's enough of that data to be worth keeping, we save it as a temp file.
       if (!inherits(stockData, "error") && length(stockData[, 1]) > 1) {
+        ## Don't want TICK.Adjusted column
+        stockData <- stockData[, -ncol(stockData)]
         
         ## Inform the user of progress.
         message(paste0("Price data for ", companyTicker, sep = ""))

### 2025-01-17 R/install_yfinance.R

@@ -1,0 +1,25 @@
+#' Install yfinance and dependencies
+#'
+#' `install_yfinance()` installs just the yfinance python package and it's
+#' direct dependencies. Users may be asked to install miniconda for the python installations. 
+#' Even if you first decline it, you can later install miniconda by running
+#' [`reticulate::install_miniconda()`]
+#' 
+#' @inheritParams reticulate::py_install
+#' 
+#' @param ... other arguments passed to [`reticulate::py_install()`]
+#' @param new_env Delete `envname` if it already exists
+#'   
+#' @importFrom reticulate py_install virtualenv_exists virtualenv_remove
+#' 
+#' @return No return value, called for installing Python yfinance module
+#' 
+#' @export
+#' 
+
+install_yfinance <- function(..., envname = "r-qmj", new_env = identical(envname, "r-qmj")) {
+  if(new_env && virtualenv_exists(envname))
+    virtualenv_remove(envname)
+    
+  py_install(packages = "yfinance", envname = envname, ...)
+}

### 2025-01-17 R/market_data.R

@@ -26,34 +26,19 @@
 #' @seealso \code{\link{market_payouts}}
 #' 
 #' @examples
-#' \dontrun{
-#' ## To immediately get quality scores using 
-#' ## package data sets.
-#' 
-#' market_data()
-#' 
-#' ## If we desire to produce a set of quality 
-#' ## scores for a specific data frame of 
-#' ## companies, which we'll call companies.
-#' 
-#' # Remove old temporary data, if present.
-#' clean_downloads(companies)
-#' 
-#' # Get raw financial and price data.
-#' raw_financials <- get_info(companies)
-#' raw_prices <- get_prices(companies)
-#' 
-#' # Clean raw data for use in market_data.
-#' financials <- tidyinfo(raw_financials)
-#' prices <- tidy_prices(raw_prices)
-#' 
-#' quality_scores <- market_data(companies, financials, prices)
+#' \donttest{
+#' # Takes more than 10 secs
+#' market_data(companies_r3k16[companies_r3k16$ticker %in% c("AAPL"), ])
 #' }
-#' @importFrom dplyr arrange %>%
-#' @import qmjdata
+#' 
+#' @importFrom dplyr arrange desc %>%
+#' @importFrom rlang .data
+#' 
+#' @return data.frame of all market data
+#' 
 #' @export
 
-market_data <- function(companies = qmjdata::companies, financials = qmjdata::financials, prices = qmjdata::prices) {
+market_data <- function(companies = qmj::companies_r3k16, financials = qmj::financials_r3k16, prices = qmj::prices_r3k16) {
   if (length(companies$ticker) == 0) {
     stop("first parameter requires a ticker column.")
   }
@@ -65,20 +50,21 @@ market_data <- function(companies = qmjdata::companies, financials = qmjdata::fi
   ## we'll call this the target-year. Since some companies may produce an 10-K filing early
   ## the next year, we'll also allow any company which produced a filing the following year
   ## through this filter.
-  target_year <- as.numeric(format(Sys.Date(), "%Y")) - 2
+  # target_year <- as.numeric(format(Sys.Date(), "%Y")) - 2
+  target_year <- max(financials$year) - 2
   leeway_year <- target_year + 1
   
-  valid_tickers <- dplyr::filter(financials, year==target_year | year==leeway_year) %>%
+  valid_tickers <- dplyr::filter(financials, .data[["year"]]==target_year | .data[["year"]]==leeway_year) %>%
                    dplyr::select(ticker) %>%
                    dplyr::distinct()
   
[…]

### 2025-01-17 R/market_growth.R

@@ -17,12 +17,13 @@
 #' @seealso \code{\link{market_payouts}}
 #' 
 #' @examples
-#' companies <- qmjdata::companies[1,]
-#' market_growth(companies, qmjdata::financials)
-#' @importFrom dplyr distinct arrange
+#' market_growth(companies_r3k16[1,], financials_r3k16)
+#' @importFrom dplyr distinct arrange desc
+#' @importFrom rlang .data
+#' @return data.frame of market growth values
 #' @export
 
-market_growth <- function(companies = qmjdata::companies, financials = qmjdata::financials) {
+market_growth <- function(companies = qmj::companies_r3k16, financials = qmj::financials_r3k16) {
   if (length(companies$ticker) == 0) {
     stop("first parameter requires a ticker column.")
   }
@@ -40,13 +41,13 @@ market_growth <- function(companies = qmjdata::companies, financials = qmjdata::
   ## We only need the first and last years of company financials to calculate growth.  In this case, order the data by year, and then grab the first
   ## instance of each ticker to appear. In order to get the last year, reverse the ordering and repeat.
   fin <- financials
-  fin <- dplyr::arrange(fin, desc(year))
+  fin <- dplyr::arrange(fin, desc(.data[["year"]]))
   
-  fstyear <- dplyr::distinct_(fin, "ticker")
+  fstyear <- dplyr::distinct(fin, .data[["ticker"]], .keep_all = TRUE)
   fstyear <- merge(allcompanies, fstyear, by = "ticker", all.x = TRUE)
   
-  fin <- dplyr::arrange(fin, year)
-  lstyear <- dplyr::distinct_(fin, "ticker")
+  fin <- dplyr::arrange(fin, .data[["year"]])
+  lstyear <- dplyr::distinct(fin, .data[["ticker"]], .keep_all = TRUE)
   lstyear <- merge(allcompanies, lstyear, by = "ticker", all.x = TRUE)
   
   ## Functions below calculate the individual components of growth for each company.

### 2025-01-17 R/market_payouts.R

@@ -17,12 +17,13 @@
 #' @seealso \code{\link{market_safety}}
 #' 
 #' @examples
-#' companies <- qmjdata::companies[1,]
-#' market_payouts(companies, qmjdata::financials)
-#' @importFrom dplyr distinct arrange
+#' market_payouts(companies_r3k16[1,], financials_r3k16)
+#' @importFrom dplyr distinct arrange desc
+#' @importFrom rlang .data
+#' @return data.frame of market payouts values
 #' @export
 
-market_payouts <- function(companies = qmjdata::companies, financials = qmjdata::financials) {
+market_payouts <- function(companies = qmj::companies_r3k16, financials = qmj::financials_r3k16) {
   
   ## Stop the function in case of bad data.
   if (length(companies$ticker) == 0) {
@@ -49,17 +50,17 @@ market_payouts <- function(companies = qmjdata::companies, financials = qmjdata:
   colnames(allcompanies) <- "ticker"
   
   fin <- financials
-  fin <- dplyr::arrange(financials, desc(year))
-  fstyear <- dplyr::distinct_(fin, "ticker")
+  fin <- dplyr::arrange(financials, desc(.data[["year"]]))
+  fstyear <- dplyr::distinct(fin, .data[["ticker"]], .keep_all = TRUE)
   
   fin <- modifiedsetdiff(fin, fstyear)
-  sndyear <- dplyr::distinct_(fin, "ticker")
+  sndyear <- dplyr::distinct(fin, .data[["ticker"]], .keep_all = TRUE)
   
   fin <- modifiedsetdiff(fin, sndyear)
-  thdyear <- dplyr::distinct_(fin, "ticker")
+  thdyear <- dplyr::distinct(fin, .data[["ticker"]], .keep_all = TRUE)
   
   fthyear <- modifiedsetdiff(fin, thdyear)
-  fthyear <- dplyr::distinct_(fthyear, "ticker")
+  fthyear <- dplyr::distinct(fthyear, .data[["ticker"]], .keep_all = TRUE)
   
   ## Forces all data frames to have the same number of rows.
   fstyear <- merge(allcompanies, fstyear, by = "ticker", all.x = TRUE)

### 2025-01-17 R/market_profitability.R

@@ -20,11 +20,13 @@
 #' @seealso \code{\link{market_payouts}}
 #' 
 #' @examples
-#' companies <- qmjdata::companies[1,]
-#' market_profitability(companies, qmjdata::financials)
+#' market_profitability(companies_r3k16[1,], financials_r3k16)
+#' @importFrom dplyr desc
+#' @importFrom rlang .data
+#' @return Whatdata.frame of market profitability values
 #' @export
 
-market_profitability <- function(companies = qmjdata::companies, financials = qmjdata::financials) {
+market_profitability <- function(companies = qmj::companies_r3k16, financials = qmj::financials_r3k16) {
   
   ## Stop function if parameters are bad.
   if (length(companies$ticker) == 0) {
@@ -42,8 +44,8 @@ market_profitability <- function(companies = qmjdata::companies, financials = qm
   allcompanies <- data.frame(companies$ticker)
   colnames(allcompanies) <- "ticker"
   fin <- financials
-  fin <- dplyr::arrange(fin, desc(year))
-  fin <- dplyr::distinct_(fin, "ticker")
+  fin <- dplyr::arrange(fin, desc(.data[["year"]]))
+  fin <- dplyr::distinct(fin, .data[["ticker"]], .keep_all = TRUE)
   fin <- merge(allcompanies, fin, by = "ticker", all.x = TRUE)
   
   ## Functions which calculate the individual profitability components.

### 2025-01-17 R/market_safety.R

@@ -17,14 +17,18 @@
 #' @seealso \code{\link{market_payouts}}
 #' 
 #' @examples
-#' \dontrun{
-#' companies <- qmjdata::companies[1,]
-#' market_safety(companies, qmjdata::financials, qmjdata::prices)
+#' \donttest{
+#' # Takes more than 10 secs
+#' market_safety(companies_r3k16[companies_r3k16$ticker %in% c("AAPL"), ])
 #' }
-#' @importFrom dplyr filter distinct arrange
+#' 
+#' @importFrom dplyr filter distinct arrange desc
+#' @importFrom stats cov lm residuals sd var
+#' @importFrom rlang .data
+#' @return data.frame of market safety values
 #' @export
 
-market_safety <- function(companies = qmjdata::companies, financials = qmjdata::financials, prices = qmjdata::prices) {
+market_safety <- function(companies = qmj::companies_r3k16, financials = qmj::financials_r3k16, prices = qmj::prices_r3k16) {
   
   if (length(companies$ticker) == 0) {
     stop("first parameter requires a ticker column.")
@@ -44,9 +48,12 @@ market_safety <- function(companies = qmjdata::companies, financials = qmjdata::
   
   prices$pret[is.nan(prices$pret)] <- 0
   prices$pret[is.infinite(prices$pret)] <- 0
-  currentyear <- as.numeric(format(Sys.Date(), "%Y"))
-  market <- dplyr::filter(prices, ticker == "GSPC")
-  nogspc <- dplyr::filter(prices, ticker != "GSPC")
+  
+  # currentyear <- as.numeric(format(Sys.Date(), "%Y"))
+  currentyear <- as.numeric(format(max(as.Date(prices$date)), '%Y'))
+  
+  market <- dplyr::filter(prices, .data[["ticker"]] == "GSPC")
+  nogspc <- dplyr::filter(prices, .data[["ticker"]] != "GSPC")
   year <- numeric()
   if (sum(as.numeric(sub("-.*", "", market$date)) == currentyear) <= 150) {
     year <- currentyear - 1
@@ -73,17 +80,17 @@ market_safety <- function(companies = qmjdata::companies, financials = qmjdata::
   }
   
   fin <- financials
-  fin <- dplyr::arrange(financials, desc(year))
-  fstyear <- dplyr::distinct_(fin, "ticker")
[…]

### 2025-01-17 R/prices_r3k16.R

@@ -1,0 +1,33 @@
+#' A dataframe of price returns and closing prices for companies in 
+#' the Russell 3000 Index
+#'
+#' Stores price returns and closing prices for the past two years 
+#' (if available) for the Russell 3000 Index companies as well as 
+#' the S&P 500 (uniquely taken from Yahoo finance), to serve as a 
+#' benchmark. For a description of the Russell 3000 index, as well as 
+#' why it was used for this package, see \code{\link{companies_r3k16}}.
+#' Last updated 2016/01/06.
+#' 
+#' Prices is used to calculate the safety score of companies, and
+#' stores closing stock prices and price returns for every company 
+#' in \code{\link{companies_r3k16}} for the past two years. Price data 
+#' varies significantly among companies, and companies that do not 
+#' return price data are not represented here. Price returns are 
+#' also calculated using two adjacent days in the dataset, a timespan
+#' which may cover one day or several depending on the company and 
+#' what day is being considered.
+#' 
+#' @format A data frame with roughly 1,500,000 rows and 4 variables
+#' \itemize{
+#'    \item ticker = Company ticker, of class \code{"character"}.
+#'    \item date = Date in format YYYY-MM-DD, of class \code{"character"}.
+#'    \item pret = Price returns, of class \code{"numeric"}.
+#'    \item close = Closing stock prices for the day, of class \code{"numeric"}.
+#'  }
+#' @source Google Finance, accessed through quantmod
+#' @name prices_r3k16
+#' @seealso \code{\link{companies_r3k16}}
+#' @seealso \code{\link{financials_r3k16}}
+#' @docType data
+#' @keywords data
+NULL

### 2025-01-17 R/qmj.R

@@ -14,18 +14,25 @@
 #' available for use.
 #' Index of datasets:
 #' \itemize{
-#'  \item companies - A data frame of publicly traded companies in the Russell 
+#'  \item companies_r3k16 - A data frame of publicly traded companies in the Russell 
 #'  3000 Index.
-#'  \item financials - Financial statements for companies in the 
-#'  companies dataset.
-#'  \item prices - Daily prices and price returns for the past two years for
+#'  \item financials_r3k16 - Financial statements for companies in the 
+#'  companies_r3k16 dataset.
+#'  \item prices_r3k16 - Daily prices and price returns for the past two years for
 #'  each company.
-#'  \item quality - Most recently measured quality z-scores and component scores.
+#'  \item quality_r3k16 - Measured quality z-scores and component scores
 #' }
 #' 
 #' @references
 #' Asness, Clifford S., Andrea Frazzini, and Lasse H. Pedersen. 'Quality Minus Junk.' AQR (2013)
 #' 
-#' @docType package
+#' @importFrom dplyr %>%
+#' @importFrom reticulate use_virtualenv
+#' 
 #' @name qmj
-NULL 
+"_PACKAGE"
+
+
+.onLoad <- function(...) {
+  use_virtualenv("r-qmj", required = FALSE)
+}

### 2025-01-17 R/quality.R

@@ -1,0 +1,36 @@
+#' A dataframe of quality scores for companies listed in the Russell 3000
+#' 
+#' Displays overall quality scores as well as the scores for profitability, 
+#' growth, safety, and payouts. Companies are sorted in order of quality 
+#' score, with NAs stored at the end of the data set. For a description of 
+#' the Russell 3000 index, as well as why it was used for this package, 
+#' see \code{\link{companies_r3k16}}. Last updated 2016/01/06.
+#' 
+#' The quality data set stores quality and component scores for the 
+#' various companies list in the \code{\link{companies_r3k16}} data set. For 
+#' every ticker in companies, quality attempts to assign a profitability, 
+#' growth, safety, and payouts score to each company using data from 
+#' \code{\link{financials_r3k16}} and \code{\link{prices_r3k16}}, and then attempts 
+#' to provide a quality score. It is possible that one or more companies 
+#' may not have sufficient information to provide one or more component 
+#' scores, in which case those companies can still be found at the end 
+#' of the data set, with NA's making up any data that cannot be found.
+#' 
+#' If partial information exists (i.e., a profitability score was able to 
+#' be calculated), then those scores are kept for that company, even if
+#' insufficient information exists to produce a quality score. More 
+#' details may be found on the technical vignette.
+#'
+#' @format A data frame with approximately 3000 rows and 7 variables
+#' \itemize{
+#'    \item quality = class \code{"numeric"}.
+#'    \item profitability = class \code{"numeric"}.
+#'    \item growth = class \code{"numeric"}.
+#'    \item safety = class \code{"numeric"}.
+#'    \item payouts = class \code{"numeric"}.
+#'  }
+#'
+#' @name quality_r3k16
+#' @docType data
+#' @keywords data
+NULL

### 2025-01-17 R/tidy_balancesheets.R

@@ -22,16 +22,27 @@
 tidy_balancesheets <- function(x) {
   
   ## Calls tidy_helper to construct a list of data.frames and merges the list elements into one large data.frame
-  balancesheets <- do.call(rbind, lapply(x, tidy_helper))
+  # balancesheets <- do.call(rbind, lapply(x, tidy_helper))
+  balancesheets <- dplyr::bind_rows(lapply(x, tidy_helper))
   
   ## Remove all rows that are solely NAs.
   balancesheets <- balancesheets[rowSums(!is.na(balancesheets)) >= 1, ]
   rownames(balancesheets) <- NULL
   
-  ## These are the categories we expect from the raw data, with abbreviations for each of the variables found in the balanceshee
-  names(balancesheets) <- c("ticker", "year", "order", "CE", "STI", "CSTI", "AR", "RE.O", "TR", "TI", "PE", "OCA", "TCA", "PPE", "AD", "GDW", "INT.N", "LTI", 
-    "OLTA", "TA", "AP", "AE", "STD", "CL", "OCL", "TCL", "LTD", "CLO", "TLTD", "TD", "DIT", "MI", "OL", "TL", "RPS", "NRPS", "CS", "APIC", "RE.AD", "TS", 
-    "OE", "TE", "TLSE", "SO", "TCSO")
+  ## These are the categories we expect from the raw data, with abbreviations for each of the variables found in the balancesheet
+  ## The wanted categories were based on previous outputs from Google Finance API which is discontinued now
+  ## So we have to map the current output (from Yahoo Finance) to previous categories
+  balancesheets <- balancesheets[, c("ticker", "year", "order", 'Preferred.Stock', 'Preferred.Stock', 'Total.Assets', 'Current.Assets', 'Current.Liabilities', 'Ordinary.Shares.Number', 'Total.Debt', 'Total.Liabilities.Net.Minority.Interest', 'Stockholders.Equity')]
+  
+  balancesheets[, -which(names(balancesheets) == "ticker")] <- 
+    lapply(balancesheets[, -which(names(balancesheets) == "ticker")], function(column) {
+      sapply(column, function(x) if (is.null(x)) NA else x)
+    })
+  balancesheets[, -which(names(balancesheets) == "ticker")] <- 
+    lapply(balancesheets[, -which(names(balancesheets) == "ticker")], as.numeric)
[…]

### 2025-01-17 R/tidy_cashflows.R

@@ -22,14 +22,17 @@
 tidy_cashflows <- function(x) {
   
   ## Calls tidy_helper to construct a list of data.frames and merges the list elements into one large data.frame
-  cashflows <- do.call(rbind, lapply(x, tidy_helper))
+  # cashflows <- do.call(rbind, lapply(x, tidy_helper))
+  cashflows <- dplyr::bind_rows(lapply(x, tidy_helper))
   
   ## Remove all rows that are solely NAs.
   cashflows <- cashflows[rowSums(!is.na(cashflows)) >= 1, ]
   rownames(cashflows) <- NULL
   
   ## These are the categories we expect from the raw data, with abbreviations for each of the variables found in the cash flows
-  names(cashflows) <- c("ticker", "year", "order", "NI.SL", "DP.DPL", "AM", "DT", "NCI", "CWC", "COA", "CX", "OICF", "CIA", "FCFI", "TCDP", "ISN", "IDN", 
-    "CFA", "FEE", "NCC", "CIP", "CTP")
+  ## The wanted categories were based on previous outputs from Google Finance API which is discontinued now
+  ## So we have to map the current output (from Yahoo Finance) to previous categories
+  cashflows <- cashflows[, c('ticker', 'year', 'order', 'Depreciation.Amortization.Depletion', 'Depreciation.And.Amortization', 'Change.In.Working.Capital', 'Changes.In.Cash', 'Cash.Dividends.Paid')]
+  names(cashflows) <- c("ticker", "year", "order", "DP.DPL", "AM", "CWC", "CX", "DIVC")
   cashflows
 } 

### 2025-01-17 R/tidy_incomestatements.R

@@ -22,16 +22,17 @@
 tidy_incomestatements <- function(x) {
   
   ## Calls tidy_helper to construct a list of data.frames and merges the list elements into one large data.frame
-  incomestatements <- do.call(rbind, lapply(x, tidy_helper))
+  # incomestatements <- do.call(rbind, lapply(x, tidy_helper))
+  incomestatements <- dplyr::bind_rows(lapply(x, tidy_helper))
   
   ## Remove all rows that are solely NAs.
   incomestatements <- incomestatements[rowSums(!is.na(incomestatements)) >= 1, ]
   rownames(incomestatements) <- NULL
   
   ## These are the categories we expect from the raw data, with abbreviations for each of the variables found in the income statements
-  names(incomestatements) <- c("ticker", "year", "order", "REV", "OREV", "TREV", "CREV", "GPROF", "SGAE", "RD", "DP.AM", "NINT", "UI", "OOE", "TOE", "OI", 
-    "INT.NNO", "GSA", "OTH", "IBT", "IAT", "MI", "EIA", "NIBEI", "AC", "DO", "EI", "NI", "PD", "IACEEI", "IACIEI", "BWAS", "BEPSEEI", "BEPSIEI", "DILADJ", 
-    "DILWAS", "DILEPSEEI", "DILEPSIEI", "DIVC", "GDIV", "NIASBCE", "BEPSSBCE", "DEPSSBCE", "DPSUP", "TSI", "NIBT", "ESIIT", "ITISI", "NIAT", "NIAC", 
-    "BNEPS", "DNEPS")
+  ## The wanted categories were based on previous outputs from Google Finance API which is discontinued now
+  ## So we have to map the current output (from Yahoo Finance) to previous categories
+  incomestatements <- incomestatements[, c('ticker', 'year', 'order', 'Net.Income.From.Continuing.And.Discontinued.Operation', 'Gross.Profit', 'Net.Income.Continuous.Operations', 'Pretax.Income', 'Net.Income', 'Net.Non.Operating.Interest.Income.Expense', 'Total.Revenue')]
+  names(incomestatements) <- c("ticker", "year", "order", "DO", "GPROF", "IAT", "IBT", "NI", "NINT", "TREV")
   incomestatements
 } 

### 2025-01-17 R/tidy_prices.R

@@ -16,18 +16,12 @@
 #' @seealso \code{\link{get_prices}}
 #' 
 #' @examples
-#' \dontrun{
-#' 
-#' sub_comps <- qmjdata::companies[1:2,]
-#' raw_price_data <- get_prices(sub_comps)
-#' prices <- tidy_prices(raw_price_data)
-#' 
 #' my_companies <- data.frame(ticker=c('GOOG', 'IBM'))
 #' raw_price_data <- get_prices(my_companies)
 #' prices <- tidy_prices(raw_price_data)
 #' 
-#' }
 #' @importFrom dplyr bind_rows %>%
+#' @return data.frame of cleaned prices
 #' @export
 
 tidy_prices <- function(x) {
@@ -46,7 +40,7 @@ tidy_prices <- function(x) {
   
   data <- lapply(1:ncol(closing), pricecombine)
   
-  #' @describeIn Convert certain columns into character in order to
+  #' Convert certain columns into character in order to
   #' bypass the warning generated by dplyr::bind_rows()
   convertcols <- function(dataframe) {
     dataframe[,1] <- as.character(dataframe[,1])  # Convert ticker to character

### 2025-01-17 R/tidyinfo.R

@@ -17,17 +17,16 @@
 #' @seealso \code{\link{tidy_incomestatements}}
 #' 
 #' @examples
-#' \dontrun{
-#' 
-#' sub_comps <- qmjdata::companies[1:2,]
-#' raw_data <- get_info(sub_comps)
-#' financials <- tidyinfo(raw_data)
-#' 
-#' my_companies <- data.frame(ticker = c('GOOG', 'IBM'))
-#' raw_data <- get_info(my_companies)
-#' financials <- tidyinfo(raw_data)
-#' 
+#' \donttest{
+#' if (reticulate::py_module_available("yfinance")) {
+#'   my_companies <- data.frame(ticker = c('GOOG', 'IBM'))
+#'   raw_data <- get_info(my_companies)
+#'   financials <- tidyinfo(raw_data)
 #' }
+#' }
+#' 
+#' @return data.frame of cleaned info (cash flows, income statements, balance sheets)
+#' 
 #' @export
 
 tidyinfo <- function(x) {
@@ -39,9 +38,15 @@ tidyinfo <- function(x) {
   financials <- merge(tidybalance, merge(tidycash, tidyincome, by = c("ticker", "order", "year")), by = c("ticker", "order", "year"))
   
   # The columns below are the only ones used in our formulas, and so the other columns are culled out.
-  keep <- c("ticker", "year", "AM", "CWC", "CX", "DIVC", "DO", "DP.DPL", "GPROF", "IAT", "IBT", "NI", "NINT", "NRPS", "RPS", "TA", "TCA", "TCL", "TCSO", 
-    "TD", "TL", "TLSE", "TREV")
+  keep <- c(
+    "ticker", "year", "order",
+    # Cash flow columns
+    "AM", "CWC", "CX", "DIVC", "DP.DPL", 
+    # Income statement columns
+    "DO", "GPROF", "IAT", "IBT", "NI", "NINT", "TREV", 
+    # Balance sheet columns 
+    "NRPS", "RPS", "TA", "TCA", "TCL", "TCSO", "TD", "TL", "TLSE")
   financials <- financials[keep]
   rownames(financials) <- NULL  # We're not interested in keeping the row numbers.
-  financials
+  financials[financials$order <= 4, ]
 } 

### 2025-01-17 R/zzz.R

@@ -1,8 +1,0 @@
-.onLoad <- function(libname, pkgname) {
-  if (system.file(package = "devtools") == "") 
-    install.packages("devtools")
-  if (system.file(package = "qmjdata") == "") {
-    devtools::install_github("anttsou/qmjdata")
-  }
-  utils::globalVariables(c("desc", "year", "ticker"))
-} 

### 2025-01-17 tests/testthat/test_financial_data_gathering_processing.R

@@ -4,19 +4,22 @@
 #' to the fullest possible extent.
 #' 
 #' RAW DATA TESTS:
-#' - Missing companies are missing specifically and only because quantmod
+#' - Missing these_companies are missing specifically and only because quantmod
 #'   does not provide data.
 #' 
 #' PROCESSED/TIDY DATA TESTS:
 #' - For any given ticker, tidied financial information has at most 4 rows.
 #'
 
-companies <- qmjdata::companies[1:3,]
-raw_fins <- qmj::get_info(companies)
-
 context("Gathering Raw Financial Data Tests")
 
-test_that("Missing companies are solely because quantmod provides no data", {
+test_that("Missing these_companies are solely because quantmod provides no data", {
+  these_companies <- companies_r3k16 %>% filter(ticker %in% c('AAPL', 'AMZN'))
+  
+  if (!reticulate::py_module_available("yfinance")) 
+    testthat::skip()
+  
+  raw_fins <- qmj::get_info(these_companies)
   
   ## If no data at all was gathered, assume internet connection is bad.
   if(length(raw_fins[[1]]) == 0)
@@ -35,10 +38,10 @@ test_that("Missing companies are solely because quantmod provides no data", {
   cf_tickers <- sapply(cf_tickers, grab_ticker)
   cf_tickers <- unique(cf_tickers)
   
-  missing_tickers <- companies$ticker[! companies$ticker %in% cf_tickers]
+  missing_tickers <- these_companies$ticker[! these_companies$ticker %in% cf_tickers]
   
   #' @describeIn Check to ensure that quantmod produces no data for missing
-  #' companies.
+  #' these_companies.
   download_check <- function(ticker){
     fin_data <- tryCatch(quantmod::getFinancials(i, auto.assign = FALSE), error = function(e) e)
     
@@ -59,6 +62,12 @@ test_that("Missing companies are solely because quantmod provides no data", {
 context("Processing/Tidying Financial Data Tests")
 
 test_that("Every ticker appears in the tidied financial data set at most four times", {
+  these_companies <- companies_r3k16 %>% filter(ticker %in% c('AAPL', 'AMZN'))
+  
+  if (!reticulate::py_module_available("yfinance")) 
+    testthat::skip()
+  
+  raw_fins <- qmj::get_info(these_companies)
   
   ## If no data at all was gathered, assume internet connection is bad.
   if(length(raw_fins[[1]]) == 0)

### 2025-01-17 tests/testthat/test_financials.R

@@ -1,15 +1,11 @@
 context("Attributes for Financials")
 
-companies <- qmjdata::companies
-financials <- qmjdata::financials
-prices <- qmjdata::prices
-
 test_that("tcso is positive", {
-  temp <- financials
+  temp <- financials_r3k16
   temp <- rbind(rep(-1, length(colnames(temp))), temp)
-  expect_error(market_data(companies,temp,prices),"Negative TCSO exists.")
-  expect_error(market_profitability(companies,temp),"Negative TCSO exists.")
-  expect_error(market_growth(companies,temp),"Negative TCSO exists.")
-  expect_error(market_safety(companies,temp,prices),"Negative TCSO exists.")
-  expect_error(market_payouts(companies,temp),"Negative TCSO exists.")
+  expect_error(market_data(companies_r3k16,temp,prices),"Negative TCSO exists.")
+  expect_error(market_profitability(companies_r3k16,temp),"Negative TCSO exists.")
+  expect_error(market_growth(companies_r3k16,temp),"Negative TCSO exists.")
+  expect_error(market_safety(companies_r3k16,temp,prices),"Negative TCSO exists.")
+  expect_error(market_payouts(companies_r3k16,temp),"Negative TCSO exists.")
 })

### 2025-01-17 tests/testthat/test_price_data_gathering_processing.R

@@ -6,7 +6,7 @@
 #' RAW DATA TESTS:
 #' - Every ticker in the raw price data is unique with a predicted number of columns.
 #' - Every ticker for which we successfully grabbed data, has some data
-#' - Missing Companies is Solely Due To Quantmod Finding No Data
+#' - Missing these_companies is Solely Due To Quantmod Finding No Data
 #' 
 #' PROCESSED DATA TESTs:
 #' - Raw data matches processed data for any given company
@@ -14,10 +14,9 @@
 
 context("Gathering Raw Price Data Tests")
 
-companies <- qmjdata::companies[1:3,]
-raw_prices <- tryCatch(qmj::get_prices(companies), error = function(e) e)
-
 test_that("Every ticker in the raw price data is unique with a predicted number of columns", {
+  these_companies <- companies_r3k16 %>% filter(ticker %in% c('AAPL', 'AMZN'))
+  raw_prices <- tryCatch(qmj::get_prices(these_companies), error = function(e) e)
   
   ## If error is returned, no internet connection.
   if(inherits(raw_prices, "error"))
@@ -43,6 +42,8 @@ test_that("Every ticker in the raw price data is unique with a predicted number 
 })
 
 test_that("Every ticker for which we successfully grabbed data, has some data", {
+  these_companies <- companies_r3k16 %>% filter(ticker %in% c('AAPL', 'AMZN'))
+  raw_prices <- tryCatch(qmj::get_prices(these_companies), error = function(e) e)
   
   ## If error is returned, no internet connection.
   if(inherits(raw_prices, "error"))
@@ -58,20 +59,22 @@ test_that("Every ticker for which we successfully grabbed data, has some data", 
   
 })
 
-test_that("Missing Companies is Solely Due To Quantmod Finding No Data", {
+test_that("Missing these_companies is Solely Due To Quantmod Finding No Data", {
+  these_companies <- companies_r3k16 %>% filter(ticker %in% c('AAPL', 'AMZN'))
+  raw_prices <- tryCatch(qmj::get_prices(these_companies), error = function(e) e)
   
   ## If error is returned, no internet connection.
   if(inherits(raw_prices, "error"))
     testthat::skip()
   
-  ## First get all companies for which we do have data.
+  ## First get all these_companies for which we do have data.
   tickers <- colnames(raw_prices)
   tickers <- gsub('\\.([^.]*$)(.*)', '', tickers)  # Remove everything after the last '.' to get rid of '.____' suffixes.
[…]

### 2025-01-17 tests/testthat/test_ticker_properties.R

@@ -1,41 +1,39 @@
 context("Ticker properties")
 
-companies <- qmjdata::companies[4:6,]
-financials <- qmjdata::financials
-prices <- qmjdata::prices
-quality <- qmjdata::quality
-
 test_that("tickers and names same in companies dataset and get_companies function",{
+  these_companies <- companies_r3k16[4:6,]
   temp <- get_companies()[4:6,]
-  expect_equal(length(intersect(companies$ticker,temp$ticker)), length(temp$ticker))
-  expect_equal(length(intersect(companies$name,temp$name)), length(temp$name))
+  expect_equal(length(intersect(these_companies$ticker,temp$ticker)), length(temp$ticker))
+  expect_equal(length(intersect(these_companies$name,temp$name)), length(temp$name))
 }) 
 
 test_that("there are no duplicate tickers",{
-    expect_equal(length(companies$ticker[duplicated(companies$ticker)]), 0)
-    expect_equal(length(quality$ticker[duplicated(quality$ticker)]), 0)
+    these_companies <- companies_r3k16[4:6,]
+    expect_equal(length(these_companies$ticker[duplicated(these_companies$ticker)]), 0)
+    expect_equal(length(quality_r3k16$ticker[duplicated(quality_r3k16$ticker)]), 0)
   })
 
 test_that("tickers identical in company and quality",{
-  temp_profitability <- market_profitability(companies,financials)
-  temp_growth <- market_growth(companies,financials)
-  temp_safety <- market_safety(companies,financials, prices)
-  temp_payouts <- market_payouts(companies,financials)
-  temp_quality <- market_data(companies, financials, prices)
-  expect_equal(length(intersect(companies$ticker,temp_quality$ticker)), length(companies$ticker))
-  expect_equal(length(intersect(companies$ticker,temp_profitability$ticker)), length(companies$ticker))
-  expect_equal(length(intersect(companies$ticker,temp_growth$ticker)), length(companies$ticker))
-  expect_equal(length(intersect(companies$ticker,temp_safety$ticker)), length(companies$ticker))
-  expect_equal(length(intersect(companies$ticker,temp_payouts$ticker)), length(companies$ticker))
+  these_companies <- companies_r3k16[4:6,]
+  temp_profitability <- market_profitability(these_companies,financials_r3k16)
+  temp_growth <- market_growth(these_companies,financials_r3k16)
[…]
